Experiences in teaching with Jupyter, Jupyterhub, and nbgrader

### 2020-01-08 paper/paper.tex
paper fixes...

At the University of Silesia, Python is used as a introductory
programming language for students of Applied Computer Science. There
has been implemented a concept of ``mobile computer classroom'' which
consists of inexpensive and mobile thin-client computers which are are
available to students in the rental office. They are used to access
compute resources where the required software is available.
Chromebooks currently play the role of thins clients, which is why all
services must be available through a web browser.  Jupyter notebook
fits perfectly in such a scenario. In recent years several work
scenarios based on Juyter notebook have been developed in such an
environment.

In the Institute of Physics, the widespread use of the Python-based
computer algebra system SageMath\cite{sagemath} system available in
the browser been started for several years. This turned out to be a
excellent solution. The Sage notebook (\texttt{sagenb}) provided
ubiquitous access to computations in science education, and a large
number of teaching materials where produced. This technology was also
replicated in partner high schools as part of the iCSE4school project
(details see \cite{icse4school}). Since 2011, c.a. 2000 students and
over 500 high school pupils have used the system. The Sage notebooks
were served using a small computer cluster and until today users
created around 30000 notebook documents which generated in peak time
over computation per second.

@@

In this paper, we will mainly concentrate on the case of course
``Introduction to Artificial Intelligence``, which is attended by
c.a. 50 Applied Computer Science students every year. The course uses
Jupyter notebook as a teaching tool during both the lectures and
tutorials. Students had to submit their work in the form of notebooks
using \texttt{nbgrader} software. Their work used automated testing to
help both students as well as teachers.

>>>>

At the University of Silesia, Python is used as a introductory
programming language for students of computer science. There has been
implemented a concept of ``mobile computer classroom'' which consists
of inexpensive and portable thin-client computers which are available
to students in the rental office. They are used to access compute
resources where the required software is available.  Chromebooks
currently play the role of thins clients, which is why all services
must be available through a web browser. Jupyter notebook fits
perfectly in such a scenario. In recent years several scenarios of
teaching workflow based on Juyter notebook have been tested and
implemented.

In the Institute of Physics, the widespread use of the Python-based
computer algebra system SageMath\cite{sagemath} system available in
the browser has been in used for several years. This turned out to be
an excellent solution. The Sage notebook (\texttt{sagenb}) provided
ubiquitous access to computations in science education, and a large
number of teaching materials where produced. This technology was also
replicated in partner high schools as part of the iCSE4school project
(details see \cite{icse4school}). Since 2011, c.a. 2000 students and
over 500 high school pupils have used the system. The Sage notebooks
have been served using a small computer cluster and until today users
have created over 30000 notebook documents.

@@

In this paper, we will mainly concentrate on the case of course
``Introduction to Artificial Intelligence``, which is attended by
c.a. 50 Applied Computer Science students every year. The course uses
Jupyter notebook as a teaching tool during both the lectures and
tutorials. Students had to submit their work in the form of notebooks
using \texttt{nbgrader} software. All excercices include automated
tests to help both students as well as teachers.
